An equivalence of compositional frameworks

### 2019-04-23 EquivCompFrameworks_20180911kc.tex
tiny

\section*{Various issues-in-progress}
{\chris If Kenny likes, we can use this as a section for all the current issues that need to be resolved, or what we are currently working on or something!}
\begin{itemize}
\item {\chris I think structured cospans should be introduced/recalled way earlier! This is a paper that compares the two,
and both should be presented early.} Sure, I'm fine with that. What section do you think we should bring it up in, or maybe create a new section entirely to mention it? {\chris I think a new section right before that equivalence section would be great!}
\end{itemize}

@@

{\chris in progress}
\begin{thm}\label{Equiv}
Let $\mathsf{A}$ and $\mathsf{X}$ be categories with (chosen) finite colimits, and $F \colon(\mathsf{A},+,0) \to (\mathbf{Cat},\times,\mathbf{1})$ a symmetric lax monoidal pseudofunctor. The symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans is equivalent to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ of structured cospans, where $L \colon \mathsf{A} \to \int{F} \cong \mathsf{X}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \int{F} \to \mathsf{A}$ by \cref{thm:Grothendieck} under the assumptions of \cref{thm:mainthmDX}.
\end{thm}
\begin{proof}
To prove this, we define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ as follows: the object component of the double functor $\mathbb{E}$ is given by $\mathbb{E}_0 = \id_{\mathsf{A}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $F\mathbb{C}\textnormal{sp}$ have objects and morphisms of $\mathsf{A}$ as objects and vertical 1-morphisms, respectively. The functor $\mathbb{E}_0$ is trivially an equivalence of categories.

>>>>

\section*{Various issues-in-progress}
{\chris If Kenny likes, we can use this as a section for all the current issues that need to be resolved, or what we are currently working on or something!}
\begin{itemize}
\item {\chris I think structured cospans should be introduced/recalled way earlier! This is a paper that compares the two,
and both should be presented early.} Sure, I'm fine with that. What section do you think we should bring it up in, or maybe create a new section entirely to mention it? {\chris I think a new section right before that equivalence section would be great!}
\item {\chris Discuss the name of Decorated and Structured cospan double categories one last time? :)}
\end{itemize}

@@

{\chris in progress}
\begin{thm}\label{Equiv}
Let $\mathsf{A}$ and $\mathsf{X}$ be categories with finite colimits, and $F \colon(\mathsf{A},+,0) \to (\mathbf{Cat},\times,\mathbf{1})$ a symmetric lax monoidal pseudofunctor. The symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans is equivalent to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ of structured cospans, where $L \colon \mathsf{A} \to \int{F} \cong \mathsf{X}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \int{F} \to \mathsf{A}$ by \cref{thm:Grothendieck} under the assumptions of \cref{thm:mainthmDX}.
\end{thm}
\begin{proof}
To prove this, we define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ as follows: the object component of the double functor $\mathbb{E}$ is given by $\mathbb{E}_0 = \id_{\mathsf{A}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $F\mathbb{C}\textnormal{sp}$ have objects and morphisms of $\mathsf{A}$ as objects and vertical 1-morphisms, respectively. The functor $\mathbb{E}_0$ is trivially an equivalence of categories.
